Improving phase-matching of FWM with temperature

### 2015-09-19 latex/article.tex
up to data aggregation

\begin{table}[ht]
\centering
  \begin{tabular}{lcccc}  
    \toprule
		& \multicolumn{3}{c}{Properties} \\
    \cmidrule(r){2-5}
    	\multirow{2}{*}{Materials}    & $\rho$ & $\kappa_{TH}$ & $C_P$ & TOC\\
  		& [\si{\kg\m^3}] & [\si{\W\per\m\per\K}] & [\si{\J\per\kg\per\K}] & [$10^{-4}$\si{\per\K}] \\
    \midrule
    Silicon (Si)			& 2329	& 130	& 700	& 1.87\\
    Silica (SiO$_2$)		& 2203	& 1.38	& 703	& 0\\
    \bottomrule
  \end{tabular}
  \label{tab_materials}
  \caption{Thermal properties of silicon and silica glass}
\end{table}

@@

Specifically, we used a polynomial expression of fifth order in wavelength and of second order in temperature ``\texttt{poly52}".

@@

Due to the intrinsic symmetry of the problem (and thus of the integrals) not all combinations of orders can produce FWM.
Only those in which the sum of the orders is an even number are interesting.
To narrow the possible sets, we chose to permit only full TE or full TM  combinations.

We eventually obtained a list of combinations and for each one we verified the conservation of energy and momentum.

\subsubsection{Conservation of energy and momentum}
Starting from the data of the effective index of each order at different wavelengths and temperatures, we evaluated the phase mismatch of all sets.
The evaluation was made on a grid of temperature and signal wavelength.

Each point was evaluated with the next system:
\[
\left\{
	\begin{array}{rl}
		\omega_I		&= 2\omega_P - \omega_S \\
		\\
		\Delta k		&= \beta_S + \beta_I - 2\beta_P \\
					&= \frac{2\pi}{\lambda_S}n_{eff}\left( \omega_s, T \right) + \frac{2\pi}{\lambda_I}n_{eff}\left( \omega_I, T \right) - 2\frac{2\pi}{\lambda_P}n_{eff}\left( \omega_P, T \right)
	\end{array}
\right.
\]
Imposing the conservation of energy, we obtained the only frequency permitted for $\omega_I$.
We replaced its value in the conservation of momentum formula, giving us the phase mismatch as a function of signal wavelength and temperature, for each set of orders.

@@

\section{Conclusions}
\subsection{Improvements}
\subsection{Results}

>>>>

\begin{table}[ht]
\centering
  \begin{tabular}{lcccc}  
    \toprule
		& \multicolumn{3}{c}{Properties} \\
    \cmidrule(r){2-5}
    	\multirow{2}{*}{Materials}    & $\rho$ & $\kappa_{TH}$ & $C_P$ & TOC\\
  		& [\si{\kg\m^3}] & [\si{\W\per\m\per\K}] & [\si{\J\per\kg\per\K}] & [\si{\per\K}] \\
    \midrule
    Silicon (Si)			& 2329	& 130	& 700	& \num{1.87e-4}\\
    Silica (SiO$_2$)		& 2203	& 1.38	& 703	& 0\\
    \bottomrule
  \end{tabular}
  \label{tab_materials}
  \caption{Thermal properties of silicon and silica glass}
\end{table}

@@

Specifically, we used a polynomial expression of fifth order in wavelength and second order in temperature ``\texttt{poly52}".

@@

Due to the intrinsic symmetry of the problem (and thus of the integrals) not all combinations of orders can produce FWM.
Only those in which the sum of the orders is an even number are interesting.
To narrow the possible sets, we chose only full TE or full TM  combinations.

We eventually obtained a list of combinations and for each one we evaluated the phase mismatch.

\subsubsection{Conservation of energy and momentum}
As it is, the phase mismatch is a function of the wavelenghts of pump, signal and idler.
Imposing the conservation of energy,
\begin{equation}
2\omega_P = \omega_S + \omega_I
\qquad \Longrightarrow \qquad
\omega_I = 2\omega_P - \omega_S \\
\end{equation}
we obtained the only frequency permitted for $\omega_I$.

We replaced its value in the conservation of momentum formula, giving us the phase mismatch as a function only of signal wavelength and temperature of the heater, for each set of orders.

Then, starting from the fits of the effective index at different wavelengths and temperatures, we evaluated the phase mismatch of all sets.
The evaluation was made on a grid of temperature and signal wavelength arbitrarily dense.

@@

\section{Results}
\section{Conclusions}
\subsection{Improvements}
\subsection{Summary}
